---
title: "ProPane Tweak: That Was the Tweak That Was"
author: "Aaron Robotham"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ProPane Tweak: That Was the Tweak That Was}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First we load the packages we will need for this vignette:

```{r}
library(ProPane)
library(Rfits)
library(magicaxis)
library(imager)
```


## Directly Tweaking Image Pixels

We will start with out usual demo image:

```{r}
image = Rfits_read_image(system.file('extdata/VIKING/mystery_VIKING_Z.fits',
  package="ProFound"))
```

```{r, fig.width=8, fig.height=8, dpi=40}
plot(image)
```

Below we shift the image by x +2, y +2 and rotate it by 5 degrees (clockwise):

```{r}
image_tran = image
image_tran$imDat = propaneTran(image_tran$imDat, 2, 2, 5)
```

And we can check this:

```{r, fig.width=8, fig.height=8, dpi=40}
plot(image_tran)
```

Now we tweak the solution (this will take about 20 seconds):

```{r}
tweak = propaneTweak(image, image_tran, delta_max=c(5,10), shift_int=FALSE)
```

Our tweaked image is pretty close to correcting for our original transform:

```{r}
best = tweak$optim_out$par
print(best)
```

We can use the output to manipulate the pixels:

```{r}
image_fix = image
image_fix$imDat = propaneTran(image_tran$imDat, best[1], best[2], best[3])
```

```{r, fig.width=8, fig.height=8, dpi=40}
plot(image_fix)
```

We can also modify the WCS rather than the image pixels:

```{r}
image_fix2 = propaneWCSmod(image_tran, best[1], best[2], best[3]) #correct WCS
```

```{r, fig.width=8, fig.height=8, dpi=40}
plot(image_fix2)
```

In the last example note how the WCS grid follows the original sources correctly.

To make all of the above easier we can request **propaneTweak** to directly modify our WCS passed in (which is the default):

```{r, fig.width=8, fig.height=8, dpi=40}
plot(tweak$image_post_fix)
```

## Directly Tweaking Image WCS

Now we will look at a case where the pixels are matched but the WCS is not:

```{r}
image_tran2 = propaneWCSmod(image, 2, 2, 5)
```

```{r, fig.width=8, fig.height=8, dpi=40}
plot(image_tran2)
```

Note we set WCS_match to FALSE since it is the WCS itself that is wrong.

The tweak of the WCS directly will takes longer than before (about 100 seconds):

```{r}
tweak2 = propaneTweak(image, image_tran2, delta_max=c(5,10), shift_int=FALSE,
  WCS_match=FALSE)
```

The answer almost perfectly corrects are adjustment to the WCS:

```{r}
print(tweak2$optim_out$par)
```

And the image and WCS looks very nice now:

```{r, fig.width=8, fig.height=8, dpi=40}
plot(tweak2$image_post_fix)
```

## What Sort of Tweak

Most of the time users will want to use the *WCS_match* = FALSE form of tweaking when trying to improve the registration of slightly offset frames for stacking. In this situation they will need to choose a reference frame to tweak all subsequent frames to, or be careful to tweak frames in the correct order so that a larger mosaic is all correctly registered.

Given the computational cost, it is often a good idea to determine tweaking based on a nice subset region of the image (ideally only a few hundred to a thousand pixels in dimension). Tweaking a very large image (8k x 8k) will take quite a long time (probably hours), but 1k x 1k should be around 10-15 minutes.
